\documentclass[]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{titling}

\onehalfspacing % reduces spacing following Headings
\posttitle{\par\end{center}\vskip 0.5em}
\setlength{\droptitle}{-60pt}
\titlespacing\subsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{0pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\singlespacing

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Curriculum Vitae - Karl Kent Benedict},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

\oddsidemargin = 0pt
\evensidemargin = 0pt
\topmargin = -36pt
\textwidth = 468pt
\textheight = 648pt

\setcounter{secnumdepth}{0}

\title{Curriculum Vitae - Karl Kent Benedict}

\begin{document}
\thetitle %\maketitle

\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\setcounter{enumi}{12}
\tightlist
\item
  \begin{enumerate}
  \def\labelenumii{(\arabic{enumii})}
  \setcounter{enumii}{504}
  \tightlist
  \item
    301-4541 \textbar{} kbene@unm.edu \textbar{} ORCID:
    \href{https://orcid.org/0000-0002-9109-2072}{0000-0002-9109-2072}
  \end{enumerate}
\end{enumerate}

\subsubsection{Education}\label{education}

July 2004, Ph.D., with Distinction, Anthropology, University of New
Mexico.\\
May 1995, M.A., with Distinction, Anthropology, University of New
Mexico.\\
May, 1986, B.A., Anthropology, University of California, Berkeley.

\subsubsection{Selected Employment/Professional
Experience}\label{selected-employmentprofessional-experience}

8/24-Present, University of New Mexico, College of University Libraries
and Learning Sciences (CUL\&LS): \emph{Emeritus Professor}

7/21-7/24, University of New Mexico, College of University Libraries and
Learning Sciences (CUL\&LS): \emph{Professor}: Director of Information
Technology, Director of Research Data Services (RDS, through 6/24),
Director of Digital Initiatives and Scholarly Communications (DISC,
6/24), Director of newly combined RDS/DISC and Learning and Outreach
Services unit (7/24).

7/14-6/21, University of New Mexico, College of University Libraries and
Learning Sciences (CUL\&LS): \emph{Associate Professor}: Director of
Information Technology (5/19-6/21), Director of Research Data Services
(7/14-6/21)

7/08-6/14, University of New Mexico, Earth Data Analysis Center:
\emph{Director} / Department of Geography: \emph{Research Assistant
Professor}

9/11-3/14, University of New Mexico, CUL\&LS: \emph{Research Assistant
Professor}

2/01-6/08, University of New Mexico, Earth Data Analysis Center:
\emph{Senior Research Scientist, Research Scientist, IT Manager}

\subsubsection{Selected Publications \&
Products}\label{selected-publications-products}

Benedict, K., \& Wheeler, J. (2022). ``Complementary Scales for
Learning, The Feedback Loop between Short-Form Technical Workshops and
Long-Form Carpentries Workshops.'' In Bauder, J. (ed.), Teaching
Research Data Management (pp.~133-151). ALA Editions, Chicago.

Molder, Edmund B., Schenkein, Sarah F., Mcconnell, Abby E., Benedict,
Karl K, \& Crista L Straub. (2022). ``Landsat Data Ecosystem Case Study:
Actor Perceptions of the Use and Value of Landsat'' Frontiers in
Environmental Science Environmental Informatics and Remote
Sensing.https://doi.org/10.3389/fenvs.2021.805174

Fundeen, J., Percivall, G., Baros, S., Baumann, P., Becker, P., Behnke,
J., Benedict, K., Colaiacomo, L., Di, L., Doescher, C., Dominguez, J.,
Edberg, R., Ferguson, M., Foreman, S., Giaretta, D., Hutchison, V. B.,
Ip, A., James, N. L., Khalsa, S. J. S., \ldots{} Young, J. (2020).
``Chapter 6: Archiving and Access Systems for Remote Sensing.'' In ASPRS
Manual of Remote Sensing (Fourth Edition, pp 451-639). American Society
for Photogrammetry and Remote Sensing

Gregory, A., Chen, C., Wu, R., Miller, S., Ahmad, S., Anderson, J. W.,
Barrett, H., Benedict, K., Cadol, D., Dascalu, S. M., Delparte, D.,
Fenstermaker, L., Godsey, S., Harris, F. C., McNamara, J. P., Tyler, S.
W., Savickas, J., Sheneman, L., Stone, M., \& Turner, M. A. (2020).
``Efficient Model-Data Integration for Flexible Modeling, Parameter
Analysis and Visualization, and Data Management.'' Frontiers in Water,
2, 21 pages. https://doi.org/10.3389/frwa.2020.00002

Benedict, K. (2017). ``The Geographic Storage, Transformation and
Retrieval Engine (GSToRE): A Platform for Active Data Access and
Publication as a Complement to Dedicated Long-Term Preservation
System.'' In Curating research data. Volume two, A handbook of current
practice (Vol. 2, pp.~207--209). Association of College and Research
Libraries.

Wheeler, Jonathan, Karl Benedict. 2015. `Functional Requirements
Specification for Archival Asset Management: Identification and
Integration of Essential Properties of Services Oriented Architecture
Products'. \emph{Journal of Map and Geography Libraries} 11(2).
pp.~155-179. DOI: 10.1080/15420353.2015.1035474.

Del Rio, N., Villanueva-Rosales, N., Pennington, D., Benedict, K.,
Stewart, A., Grady, C. J. (2013). ``ELSEWeb Meets SADI: Supporting
Data-to-Model Integration for Biodiversity Forecasting.'' Paper
presented at Discovery Informatics: AI Takes a Science-Centered View on
Big Data. AAAI Technical Report FS-13-01. pp 8-15.

Qunying Huang, Chaowei Yang, Karl Benedict, Abdelmounaam Rezgui, Jibo
Xie, Jizhe Xia Songqing Chen. 2012. `Using adaptively-coupled models and
high performance computing for enabling the computability of dust storm
forecasting'. \emph{International Journal of Geographical Information
Science}. 27(4):765-784. DOI:10.1080/13658816.2012.715650.

Huang, Qunying, Jizhe Xia, Manzhu Yu, Karl Benedict, and Myra Bambacus.
2013. `Cloud-enabled Dust Storm Forecasting', in \emph{Spatial Cloud
Computing, a Practical Approach}. Chaowei Yang and Qunying Huang,
eds.~CRC Press. {[}http://dx.doi.org/10.1201/b16106-14{]}{[}12{]}

Benedict, K. (2017). `The Geographic Storage, Transformation and
Retrieval Engine (GSToRE): A Platform for Active Data Access and
Publication as a Complement to Dedicated Long-Term Preservation System'.
In \emph{Curating research data. Volume two, A handbook of current
practice} (Vol. 2, pp.~207--209), Lisa R. Johnston, ed.~Chicago, IL:
Association of College and Research Libraries.

``Geographic Storage, Transformation and retrieval Engine Version 3''.
2013. Geospatial data management, discovery and access platform and
associated Application Programming Interface. Developed by the
development team at the Earth Data Analysis Center at the University of
New Mexico under the direction of Karl Benedict.

``Data Management Training Clearinghouse (DMTC).'' 2020 - 2023. Curated
clearinghouse for distributed research data management training
materials accessible over the web.
https://dmtclearinghouse.esipfed.org/. Related software releases: a.
Barrett, Hays, Benedict, Karl, Hoebelheinrich, Nancy, \& Wong, Mona.
(2023). Application Programming Interface code for the Data Management
Training Clearinghouse (0.1.0-2022-07ESIPDemo). Zenodo.
https://doi.org/10.5281/zenodo.7787156; b. Benedict, Karl, Wong, Mona,
Hoebelheinrich, Nancy, \& Barrett, Hays. (2023). User interface code for
the Data Management Training Clearinghouse (0.1.0-2022- 07ESIPDemo).
Zenodo. https://doi.org/10.5281/zenodo.7787157

\subsubsection{Selected Synergistic
Experience}\label{selected-synergistic-experience}

2019 - Present, Earth Science Information Partners (ESIP) Group on Earth
Observations (GEO) alternate Programme Board Representative, GEO Data
Working Group, and GEOSS Infrastructure Development Task Team.\\
2019 - Present, Certified \emph{Carpentries Instructor}
(2/2019-Present), \emph{Carpentries Instructor Trainer} (4/2022 -
Present).\\
2017 - Present, DataONE Management Team member.\\
2012-14, 2019-2020, \emph{President}, Earth Science Information Partners
(ESIP).\\
2015 - 2018, \emph{Technical Advisory Committee} (Chair), Digital
Preservation Network\\
2011 - 2014, \emph{Member of the Data Management and Communications
(DMAC) Steering Committee} of the Interagency Ocean Observation
Committee (IOOC)\\
2010 - 2012, \emph{Member of the National Advisory Council for
Environmental Policy and Technology} for the US Environmental Protection
Agency (EPA)

\end{document}
